\documentclass[12]{article}
\begin{document}
\begin{titlepage}
\begin{center}
\line(1,0){150}\\
\huge{\bfseries AFIELD ATTACHMENT REPORT CONDUCTED AT WEB INFO-NET LIMITED}\\
\line(1,0){100}\\
\end{center}
\begin{flushright}
\textsc{\LARGE Mugumya Leonalds\\
RESEARCH METHODOLOGY\\
214017217\\
14/u/9560/ps\\
march29,2017\\}
\end{flushright}
\end{titlepage}
\section{introduction}
Field attachment aims at providing students with an opportunity to apply the principle and techniques theoretically learnt into real life problem solving situations and also get hands on experience about the real life work situations. The purpose of this field attachment report is to provide documentation of all the activities, tasks and practical training I carried out during the internship training period at Web Info-Net Limited from 6th June 2016 to 6th August 2016. The activities included;
\subsection{Computer Hardware Repair and Software Maintenance }
Hard ware are tangible electronic components of a computer, software are instructions that direct a computer user on what to do. Under computer hardware repair and software maintenance. this is what was involved;
Identifying different parts of the computer and their functions. Dismantling and assembling of computer system unit, hardware troubleshooting techniques and maintenance strategies.
\subsection{networking}
Under networking this is what was involved; Sharing the folder Sharing, the compact disk(CD) drive, Remote desktop access, Drawing computer network plans, surveys and bureau of quantity
\subsection{Server Administration }
Under server administration this is what was involved; Introduction and installation of windows server 2008, Configuring and installation of domain name service(DNS), active directory domain service(ADDS), Configuring and installation of file server and terminal services, Sharing the public folder.
\subsection{ubuntu 14.04/linux distribution }
Under Ubuntu 14.04/Linux distribution this is what was involved; Deleting files and directories, adding and deleting user accounts, ls-al-formatted listing using hidden files.
\subsection{network security}
This involved the following activities; Sniffing and snoofing that is listening and analyzing the data later using the wire shark software, spoofing for example viewing some body’s’ passwords for emails, Facebook accounts.
\section{Experience And Skills.}
Computer hardware and software maintenance skills, Networking Administration and Security skills.
\section{challenges}
High transport costs, Limited time for training
\section{Recommendations }
I recommend that internship training should be done twice by the intern students so that they can acquire more skills in the field as it basically focus on practical skills than theoretical skills also i recommend that Makerere University, School of Computing should give field attachment allowances to students in time to allow them make thorough preparations for the field attachment period.
\section{Conclusion.}
This internship was definitely an introduction to the actual work field for me. The industrial training at Web Info-Net Limited was definitely a learning experience that I will live to recognize throughout my learning experience.
This internship was definitely beneficial to me and I am grateful and thankful that I got the experience that will help me in the nearby future.
\section{ReferenceS.}
CCNA portable command guide Guide Second Edition by scott Empson.
Http://www.webinfo.net.co.ug
Linux pocket Guide by O’ReillyBeginners Guide to SQL Server2008 by Dušan Petkovic Http://www.brainshare.com
\end{document}
